Fail Faster

### 2025-03-20 paper/paper.tex
pauls eval wibbles

\bcp{Feels like we're missing a trick in the transition here.  Can we
  say, ``Because performance is important, PBT libraries are already
  quite tuned.  [Can we substantiate that??]  But more is
  possible...'' }

@@

All experiments were run on a 64-bit Linux machine with 264 GB RAM and an Intel Xeon Platinum 8375C CPU, running Ubuntu 24.04.1 LTS. \camlname and all OCaml benchmarks
were compiled with 4.14.1+BER MetaOCaml \texttt{ocamlopt}, the native code compiler for OCaml, using compiler flag \texttt{-O3}.
The baseline OCaml generators were written with \bq{} 0.16.
\scalaname{} and all Scala benchmarks
were run on Scala 3.6.3
and OpenJDK 21.0.6, using ScalaCheck version 1.17 as the baseline.
We used \texttt{core\_bench} 0.16 \cn in OCaml and \texttt{jmh} 0.4.7 \cn for generator performance microbenchmarking.

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.32]{scala.png}
 \caption{\scalaname has better performance relative to ScalaCheck than \camlname relative to \bq. SC is ScalaCheck; BQ is \bq. Comparison is for a fixed size of 100.}
 \label{fig:scala}
 \end{figure}

>>>>

@@

All experiments were run on a 64-bit Linux machine with 264 GB RAM and a 128-core Intel Xeon Platinum 8375C CPU, running Ubuntu 24.04.1 LTS. \camlname and all OCaml benchmarks
were compiled with 4.14.1+BER MetaOCaml \texttt{ocamlopt}, the native code compiler for OCaml, using compiler flag \texttt{-O3}.
The baseline OCaml generators were written with \bq{} 0.16.
\scalaname{} and all Scala benchmarks
were run on Scala 3.6.3
and OpenJDK 21.0.6, using ScalaCheck version 1.17 as the baseline.
We used \texttt{core\_bench} 0.16 \cn in OCaml and \texttt{jmh} 0.4.7 \cn for generator performance microbenchmarking.

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.32]{scala.png}
 \caption{
  \jwc{Don't explain the chart in the caption, split this into two different charts --- purple on one, green on the other.}
  \jwc{Also can we use the language's colors for this?}
  \scalaname has better performance relative to ScalaCheck than \camlname relative to \bq. SC is ScalaCheck; BQ is \bq. Comparison is for a fixed size of 100.}
 \label{fig:scala}
 \end{figure}
